---
title: analysis of ING-only and HRT-only stims
output: html_document
---

# CH3: Offline categorical selections for (ING) and (HRT) in Experiments 2 and 3
**Experiment 2:** (ING) stims only

**Experiment 3:** (HRT) stims only

The csv called here is already preprocessed (attention checked, etc.)

## Prelims

```{r}
library(tidyverse)
library(brms)
library(bayestestR)
library(see) #for plotting
library(lme4)
library(emmeans)
library(sjPlot)
source("../analysis_helpers/preprocessing_singlespeaker.R")
source("../analysis_helpers/visualizing_singlespeaker.R")
source("../analysis_helpers/stan_utility.R")
source("../analysis_helpers/helpers.R")

## Get data

```{r}
cat_data <- read.csv('../../data/categorical_exp_data.csv')
```

```{r}
cat_data <- cat_data %>% filter(criticality == 'CRITICAL') # we're not interested in fillers 
cat_data$condition <- factor(cat_data$condition, levels = c('Declarative' , 'HRT', 'ing', 'in'))
cat_data$styletype <- factor(cat_data$styletype, levels = c('(HRT)', '(ING)'))


```

## Make dfs

```{r}
exp2_tough.df <- cat_data %>%
  filter(expcode == 2, styletype == '(ING)') 
exp2_tough.df$c_condition <- myCenter(exp2_tough.df$condition)

exp3_valley.df <- cat_data %>%
  filter(expcode == 3,  styletype == '(HRT)') 
exp3_valley.df$c_condition <- myCenter(exp3_valley.df$condition)
```


## Model

### TOUGHS

#### Weakly informative priors
See eg https://discourse.mc-stan.org/t/default-priors-for-logistic-regression-coefficients-in-brms/13742/4 and McElreath 2020

```{r}
exp2_tough.modInform <- brm(target_selection ~ condition + left_choice_type + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp2_tough.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                                iter = 5000,
                               seed = 12345, #w default (2000 iter, rhat)
                               control = list(adapt_delta = 0.99, max_treedepth = 15))

#set_prior("<prior>",class = "b"). T
#coef = "x2"
```

```{r}
saveRDS(exp2_tough.modInform, file = '../../models/exp2_tough.modInform.Rds')
```

```{r}
exp2_tough.modInform <- readRDS('../../models/exp2_tough.modInform.Rds')
```

```{r}
summary(exp2_tough.modInform)
exp2_tough.modInform_posterior_summ <- describe_posterior(exp2_tough.modInform, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```


```{r}
make_post_summ_table(exp2_tough.modInform_posterior_summ)
```


### VALLEYS

#### Weakly informative priors
See eg https://discourse.mc-stan.org/t/default-priors-for-logistic-regression-coefficients-in-brms/13742/4 and McElreath 2020

```{r}
exp3_valley.modInform <- brm(target_selection ~ condition + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp3_valley.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345) #w default (2000 iter, rhat)
                               #control = list(adapt_delta = 0.99, max_treedepth = 15))

#set_prior("<prior>",class = "b"). T
#coef = "x2"
```

```{r}
saveRDS(exp3_valley.modInform, file = '../../models/exp3_valley.modInform.Rds')
```

```{r}
exp3_valley.modInform <- readRDS('../../models/exp3_valley.modInform.Rds')
```

```{r}
summary(exp3_valley.modInform)
exp3_valley.modInform_posterior_summ = describe_posterior(exp3_valley.modInform, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
exp3_valley.modInform_posterior_summ
```


```{r}
make_post_summ_table(exp3_valley.modInform_posterior_summ)
```




# Trial order

```{r}
exp2_tough_trial.plot <- plot_categorical_selections_by_trial_n(exp2_tough.df, toughPalette)
```

```{r}
exp2_tough_trial.plot
```

```{r}
exp2_tough_halves.df <- exp2_tough.df %>%
mutate(half = as.factor(ifelse(trial_no <= 14, 'first', 'second')))
```

```{r}
exp2_tough_half.mod <-  brm(target_selection ~ condition*half + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp2_tough_halves.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345, #w default (2000 iter, rhat)
                               control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
saveRDS(exp2_tough_half.mod, file = "../../models/exp2_tough_half.mod.Rds")
```

```{r}
exp2_tough_half.mod <- readRDS("../../models/exp2_tough_half.mod.Rds")
```

```{r}
summary(exp2_tough_half.mod)
exp2_tough_half_posterior_summ = describe_posterior(exp2_tough_half.mod, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
exp2_tough_half_posterior_summ 
```

```{r}
make_post_summ_table(exp2_tough_half_posterior_summ )

````
#### Now Valleys

```{r}
exp3_valley_trial.plot <- plot_categorical_selections_by_trial_n(exp3_valley.df, valleyPalette)
```

```{r}
exp3_valley_trial.plot
```

```{r}
exp3_valley_halves.df <- exp3_valley.df %>%
mutate(half = as.factor(ifelse(trial_no <= 14, 'first', 'second')))
levels(exp3_valley_halves.df$half)
```

```{r}
exp3_valley_half.mod <-  brm(target_selection ~ condition*half + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp3_valley_halves.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345, #w default (2000 iter, rhat)
                               control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
saveRDS(exp3_valley_half.mod, file = "../../models/exp3_valley_half.mod.Rds")
```

```{r}
exp3_valley_half.mod <- readRDS("../../models/exp3_valley_half.mod.Rds")
```

```{r}
summary(exp3_valley_half.mod)
exp3_valley_half_posterior_summ = describe_posterior(exp3_valley_half.mod, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
exp3_valley_half_posterior_summ 
```

```{r}
make_post_summ_table(exp3_valley_half_posterior_summ )
```

