---
title: Comparing multiple exps
output: html_document
---

# CH3: Offline categorical selections for (HRT) and (ING) across multiple exps


The csv called here is already preprocessed (attention checked, etc.)

## Prelims

```{r}
library(tidyverse)
library(brms)
library(bayestestR)
library(see) #for plotting
library(sjPlot)
library(emmeans)
library(see) #for plotting
source("../analysis_helpers/preprocessing_singlespeaker.R")
source("../analysis_helpers/visualizing_singlespeaker.R")
source("../analysis_helpers/stan_utility.R")
source("../analysis_helpers/helpers.R")
options(scipen=999)
```

## Get data

```{r}
cat_data <- read.csv('../../data/categorical_exp_data.csv')
```

```{r}
cat_data <- cat_data %>% filter(criticality == 'CRITICAL') # we're not interested in fillers 
cat_data$condition <- factor(cat_data$condition, levels = c('Declarative' , 'HRT', 'ing', 'in'))
cat_data$styletype <- factor(cat_data$styletype, levels = c('(HRT)', '(ING)'))
```

# Toughs

## compare exp 1 vs exp 2

aka Random order vs solo cue: in write up, random order is exp3, solo cue is exp 1

```{r}
exp12_tough.df <- cat_data %>%
  filter(expcode == 1 | expcode == 2,  styletype == '(ING)') 

exp12_tough.df$f_expcode <- as.factor(exp12_tough.df$expcode)
exp12_tough.df$f_expcode <- relevel(exp12_tough.df$f_expcode, ref= "2")
levels(exp12_tough.df$f_expcode)
```

```{r}
exp12_tough.modInform <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp12_tough.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                             cores = 8,
                                iter = 5000,
                               seed = 12345, #w default (2000 iter, rhat)
                               control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
saveRDS(exp12_tough.modInform, file = "../../models/exp12_tough.modInform.Rds")
```

```{r}
exp12_tough.modInform <- readRDS("../../models/exp12_tough.modInform.Rds")
```

```{r}
summary(exp12_tough.modInform )
exp12_tough.modInform_post_summ <- describe_posterior(exp12_tough.modInform , centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
exp12_tough.modInform_post_summ
```

```{r}
make_post_summ_table(exp12_tough.modInform_post_summ)
```



### compare exp 1 and 2 in' only

```{r}
exp12_in.df <- exp12_tough.df %>%
filter(condition == 'in')
```

```{r}
exp12_in.mod <- brm(target_selection ~ f_expcode + (1|participant) + (1|stim_type), 
                               family="bernoulli", 
                               data= exp12_in.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                             #cores = 8,
                                #iter = 5000,
                               seed = 12345) #w default (2000 iter, rhat)
                               #control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
summary(exp12_in.mod)
describe_posterior(exp12_in.mod, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```

## Compare exp 4 vs exp 5 

```{r}
exp45_tough.df <- cat_data %>%
  filter(styletype == '(ING)', expcode == 4 | expcode == 5)
exp45_tough.df$f_expcode <- as.factor(exp45_tough.df$expcode)
```

```{r}
exp45_tough.mod <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp45_tough.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345,
                               control = list(adapt_delta = 0.99))
```

```{r}
saveRDS(exp45_tough.mod, file = "../../models/exp45_tough.mod.Rds")
```

```{r}
exp45_tough.mod <- readRDS("../../models/exp45_tough.mod.Rds")
```

```{r}
summary(exp45_tough.mod)
exp45_tough.mod_post_summ <- describe_posterior(exp45_tough.mod, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```

```{r}
make_post_summ_table(exp45_tough.mod_post_summ)
```



```{r}
plot_model(exp45_tough.mod, type = "int")
emmip(exp45_tough.mod, condition ~ f_expcode, CIs=TRUE, plotit=T)+theme_bw()
```

## Compare all exps

```{r}
tough.df <- cat_data %>%
  filter(styletype == '(ING)')

tough.df$f_expcode <- as.factor(tough.df$expcode)
tough.df$f_expcode <- relevel(tough.df$f_expcode, ref='2')
```

```{r}
tough.mod <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= tough.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345,
                               control = list(adapt_delta = 0.99))
```

```{r}
saveRDS(tough.mod, file = "../../models/tough.mod.Rds")
```

```{r}
tough.mod <- readRDS("../../models/tough.mod.Rds")
```

```{r}
summary(tough.mod)
tough_post_summ <- describe_posterior(tough.mod, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```


```{r}
make_post_summ_table(tough_post_summ)
```

# Valleys

## Compare exp 1 vs exp 3

```{r}
exp13_valley.df <- cat_data %>%
  filter(expcode == 1| expcode == 3,   styletype == '(HRT)') 

exp13_valley.df$f_expcode <- as.factor(exp13_valley.df$expcode)
```

```{r}
exp13_valley.modInform <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp13_valley.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 10000,
                               seed = 12345) #w default (2000 iter, rhat)
                               #control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
saveRDS(exp13_valley.modInform, file = "../../models/exp13_valley.modInform.Rds")
```

```{r}
exp13_valley.modInform <- readRDS("../../models/exp13_valley.modInform.Rds")
```

```{r}
summary(exp13_valley.modInform )
describe_posterior(exp13_valley.modInform , centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```

## Compare exp 3 vs exp 4

```{r}
exp34_valley.df <- cat_data %>%
  filter(expcode == 3 | expcode == 4,  styletype == '(HRT)') 

exp34_valley.df$f_expcode <- as.factor(exp34_valley.df$expcode)
```

```{r}
exp34_valley.modInform <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp34_valley.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345) #w default (2000 iter, rhat)
                               #control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
summary(exp34_valley.modInform)
describe_posterior(exp34_valley.modInform, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```

## Compare exp 4 vs exp 5

```{r}
exp45_valley.df <- cat_data %>%
  filter(expcode == 4 | expcode == 5,  styletype == '(HRT)') 

exp45_valley.df$f_expcode <- as.factor(exp45_valley.df$expcode)
```

```{r}
exp45_valley.modInform <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= exp45_valley.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 7500,
                             cores = 8,
                               seed = 12345) #w default (2000 iter, rhat)
                               #control = list(adapt_delta = 0.99, max_treedepth = 15))
```

```{r}
saveRDS(exp45_valley.modInform, file = "../../models/exp45_valley.modInform.Rds")
```

```{r}
exp45_valley.modInform <- readRDS("../../models/exp45_valley.modInform.Rds")
```

```{r}
summary(exp45_valley.modInform)
exp45_valley_post_summ  <- describe_posterior(exp45_valley.modInform, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
exp45_valley_post_summ 
```

```{r}
make_post_summ_table(exp45_valley_post_summ)
 
```


```{r}
plot_model(exp45_valley.modInform, type = "int")
emmip(exp45_valley.modInform, condition ~ f_expcode, CIs=TRUE, plotit=T)+theme_bw()
```

## Compare all exps

```{r}
valley.df <- cat_data %>%
  filter(styletype == '(HRT)')

valley.df$f_expcode <- as.factor(valley.df$expcode)
valley.df$f_expcode <- relevel(valley.df$f_expcode, ref='3')
```

```{r}
valley.mod <- brm(target_selection ~ condition*f_expcode + (1+condition|participant) + (1+condition|stim_type), 
                               family="bernoulli", 
                               data= valley.df,
                                 prior = c(prior(normal(0, 2), class = b)),
                               #prior = c(prior(normal(0, 2), class = Intercept), prior(normal(0, 2), class = b)),
                                iter = 10000,
                             cores = 8,
                               seed = 12345,
                               control = list(adapt_delta = 0.99))
```

```{r}
saveRDS(valley.mod, file = "../../models/valley.mod.Rds")
```

```{r}
valley.mod <- readRDS("../../models/valley.mod.Rds")
```

```{r}
summary(valley.mod)
describe_posterior(valley.mod, centrality = "MAP", test = c("p_direction","rope"), ci=0.95, rope_ci=1)
```

```{r}
gender.plot  <- cat_data %>%
filter(gender != 'Other')%>%
    group_by(condition, gender) %>%
    summarize(mean_cat_selection = mean(target_selection),
              CI.Low = ci.low(target_selection), 
              CI.High = ci.high(target_selection))%>%
    mutate(YMin = mean_cat_selection - CI.Low, 
           YMax = mean_cat_selection + CI.High) %>%
    ggplot( aes(x=condition, y=mean_cat_selection, fill = condition))+
    geom_bar(position=position_dodge(), stat = "identity") +
    geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25, position=position_dodge(.9)) +
    #scale_fill_manual(values=palette) + 
    ylab("Proportion of Tough Selections") +
    ylim(0, 1) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(color="black", size=16),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(color="black", size=16),
          legend.title = element_text(color="black", size=16),
          legend.text = element_text(color="black", size=14))+
facet_grid(~gender)
```

```{r}
gender.plot
```

```{r}
gender.plot  <- cat_data %>%
filter(gender != 'Other')%>%
    group_by(condition, gender) %>%
    summarize(mean_cat_selection = mean(target_selection),
              CI.Low = ci.low(target_selection), 
              CI.High = ci.high(target_selection))%>%
    mutate(YMin = mean_cat_selection - CI.Low, 
           YMax = mean_cat_selection + CI.High) %>%
    ggplot( aes(x=condition, y=mean_cat_selection, fill = condition))+
    geom_bar(position=position_dodge(), stat = "identity") +
    geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25, position=position_dodge(.9)) +
    #scale_fill_manual(values=palette) + 
    ylab("Proportion of Tough Selections") +
    ylim(0, 1) +
    theme(axis.title.x = element_blank(),
          axis.text.x = element_text(color="black", size=16),
          axis.text.y = element_text(size = 14),
          axis.title.y = element_text(color="black", size=16),
          legend.title = element_text(color="black", size=16),
          legend.text = element_text(color="black", size=14))+
facet_grid(~gender)
```

#just want std dev

```{r}
summary_data <- cat_data%>%
  filter(criticality == 'CRITICAL') %>%
  group_by(condition) %>%
  summarize(mean_tscore = mean(cat_selection), std_dev_tscore = sd(cat_selection))

summary_data
```

