---
title: "Ch.3: Offline Categorical Selections for (ING) and (HRT) - PREPROCESSING"
output: html_notebook
---

---
```{r}
library(tidyr)
library(ggplot2)
library(lme4)
library(lmerTest)
library(stringr)
library(optimx)
library(dfoptim)
library(insight)
library(jtools)
personaPalette <- c("#E69F00",  "#ffdf98", "#56B4E9","#9bd3f2")
source("../../../analysis_helpers/preprocessing_singlespeaker.R")
source("../../../analysis_helpers/visualizing_singlespeaker.R")
source("../../../analysis_helpers/helpers.R")
```

Get data
```{r}
exp1_random <- read.csv("../../data/exp1_tidy.csv")
exp2_tough <- read.csv(".../../data/exp2_tidy.csv")
exp3_valley <- read.csv("../../data/exp3_tidy.csv")
exp4_tv <- read.csv("../../data/exp4_tidy.csv")
exp5_vt <- read.csv("../../data/exp5_tidy.csv")
```

```{r}
exp1_random.tidy <- exp1_random %>%
  mutate(exptype = 'exp1_random',
         expcode = 1)
exp2_tough.tidy <- exp2_tough %>%
  mutate(exptype = 'exp2_exp3_solo_cue',
         expcode = 2)
exp3_valley.tidy <- exp3_valley %>%
  mutate(exptype = 'exp2_exp3_solo_cue', 
         expcode = 3)
exp4_tv.tidy <- exp4_tv %>%
  mutate(exptype = 'exp4_tv_ordered',
         expcode = 4)
exp5_vt.tidy <- exp5_vt %>%
  mutate(exptype = 'exp5_vt_ordered',
         expcode = 5)

expdata <- exp1_random.tidy %>%
  bind_rows(exp2_tough.tidy) %>%
  bind_rows(exp3_valley.tidy)%>%
  bind_rows(exp4_tv.tidy) %>%
  bind_rows(exp5_vt.tidy)

expdata <- expdata %>%
 mutate(stim_type = tolower(gsub("_\\w{2,4}_\\d{1}_\\w{2,4}_\\d{1}", '', trial)),
        stim_type_short = str_extract(stim_type, "[[:alpha:]]+$"),
        participant = paste(expcode, participant, sep='_'),
        styletype = ifelse(condition == 'in' | condition == 'ing', '(ING)',
                           ifelse(condition == 'HRT' | condition == 'Declarative', '(HRT)', 'Filler')))

expdata$condition <- factor(expdata$condition, levels = c('in', 'ing', 'HRT', 'Declarative', 'F', 'M'))
expdata$participant <- as.factor(expdata$participant)


# We are going to Tough-target code the HRT stims - s.t. they are on the same scale as the ING stims. 
# That is; target-selection == 1 when people click a Tough (after hearing HRT / Decl) and 0 with a valley
expdata <- expdata %>%
  mutate(v_target_selection = ifelse(styletype == '(HRT)', cat_selection,
                                  ifelse(styletype == 'ING' & cat_selection == 1, 0, 1)),
         target_selection = ifelse(styletype == '(HRT)' & cat_selection == 1, 0, 
                                ifelse(styletype == '(HRT)' & cat_selection == 0, 1, cat_selection)))


```

# Just check all exclusions are same for all exps

```{r}
ggplot(expdata, aes(x = participant_filler_score)) +
  geom_histogram()

ggplot(expdata, aes(x = participant_scene_score)) +
  geom_histogram()

test <- expdata %>%
  ungroup %>%
  filter(participant_filler_score< 13) %>%
  filter(language != "1", language != "2", language != "3", language != "4", language != "Nancy", language != "Chinese", language != "Romanian") %>%
  filter(participant_scene_score > 5) %>% #otherwise will distort the mean and come on, if you are getting below 5 you aren't doing the task right
  summarize(mean_filler = mean(participant_filler_score), 
            mean_scene = mean(participant_scene_score),
            sd_filler = sd(participant_filler_score),
            sd_scene = sd(participant_scene_score)) %>%
  mutate(filler_cut_off = mean_filler-(3*sd_filler),
         scene_cut_off = mean_scene - (3*sd_scene))
test



expdata.clean <- expdata %>%
  filter(participant_filler_score >= 11, participant_scene_score >= 23) %>%
  filter(language != "1", language != "2", language != "3", language != "4", language != "Nancy", language != "Chinese", language != "Romanian") %>%
  group_by(participant, expcode) %>% 
  mutate(n_obs = n()) %>%
  filter(n_obs < 25) %>% # some people managed to take more than once/submitted more than once; exclude entirely (nb i think this was a mturk-side bug, have tried looking for it)
  select(-n_obs) %>%
  ungroup() 


n_distinct(expdata.clean$participant) #1024 just lg, #408 harshest, #604 less harsh, #682 least harsh
# 4 dupes
# 24 language
# 189 filler  >= 11
# 169 filler  >= 10
# 333 scene score >= 22
# 422 scene score >= 23
n_distinct(expdata$participant) # 1052

 n_distinct(expdata$participant) - n_distinct(expdata.clean$participant) 
```











#Do people choose tough/valley more often when t/v is on left (or right) side? ie, does img position have an effect on cue-congruent categorizations?
if not, then it doesn't matter so much if there are unequal numbers in img-position flipped lists - so long as same numbers for each cue-style condiiton
```{r}

tough.df <- expdata %>%
  filter(styletype == '(ING)')
all_tough_exps_position.plot <- plot_categorical_selections(tough.df, toughPalette, left_choice_type)
all_tough_exps_position.plot

valley.df <- expdata %>%
  filter(styletype == '(HRT)')
all_valley_exps_position.plot <- plot_categorical_selections(valley.df, valleyPalette,left_choice_type)
all_valley_exps_position.plot

tough.mod.pos <- glmer(cat_selection ~ condition  + left_choice_type + (1|participant) + (1|exptype)+ (1|stim_type)  + (1+condition|participant), control = glmerControl(optimizer ="bobyqa"), family = binomial, data = tough.df)
summary(tough.mod.pos)#no effect of left-choice-type
vif.mer(tough.mod.pos)

valley.mod.pos <- glmer(cat_selection ~ condition  + left_choice_type + (1|participant) + (1|exptype)+ (1|stim_type) + (1+condition|participant), control = glmerControl(optimizer ="bobyqa"), family = binomial, data = valley.df)
summary(valley.mod.pos) #no effect of left-choice-type
vif.mer(valley.mod.pos)
```



#Explists - make sure they are balanced!
```{r}
expdata_unbalanced <- expdata

explist.df <- expdata %>%
  select(participant, expcode, exp_list) %>%
  unique() %>%
  group_by(expcode, exp_list) %>%
  summarize(n = n())

# lets just focus on main explists - ie ignore L/R T/V ordering - as this doesn't seem to make a difference in selections
expdata.mainlists <- expdata %>%
  group_by(expcode) %>%
  mutate(total_exp_lists = max(exp_list)) %>%
  ungroup() %>%
  mutate(main_exp_list = ifelse(total_exp_lists == 8 & exp_list > 4, exp_list-4,
                                ifelse(total_exp_lists == 4 & exp_list > 2, exp_list-2, exp_list)))

main_explist.df <- expdata.mainlists %>%
  select(participant, exp_list, expcode, main_exp_list) %>%
  unique() %>%
  group_by(expcode, main_exp_list) %>%
  mutate(n = n())
main_explist.df

expdata.equal <- expdata.mainlists %>%
  select(participant, expcode, main_exp_list) %>%
  unique() %>%
  group_by(expcode, main_exp_list) %>%
  arrange(participant) %>%
  mutate(n = row_number(), n_ppts = max(n)) %>%
  ungroup () %>%
  group_by(expcode) %>%
  filter(n <= min(n_ppts))


expdata <- semi_join(expdata.mainlists, expdata.equal)

test <- expdata_unbalanced%>%
  filter(criticality == 'CRITICAL') %>%
  group_by(expcode, stim_type, condition, styletype) %>%
  summarize(n_obs = n()) 
test
View(test)

# how many we lose if total baalnce?
total_balanced.lists <- expdata %>%
  select(participant, exp_list, expcode) %>%
  unique() %>%
  group_by(expcode, exp_list) %>%
  mutate(n = n()) %>%
  group_by(expcode, exp_list) %>%
  arrange(participant) %>%
  mutate(n = row_number(), n_ppts = max(n)) %>%
  ungroup () %>%
  group_by(expcode) %>%
  filter(n <= min(n_ppts))
total_balanced.lists
  
```

# Save csv
```{r}
write.csv(expdata, '../data/categorical_exp_data.csv')
write.csv(expdata_unbalanced, '../data/categorical_exp_data_unbalanced.csv')
```




#metadata for writeup

## time taken
```{r}
expdata.timetaken <- expdata %>%
  select(participant, time_in_minutes) %>%
  unique() %>%
  summarize(mean_tt = mean(time_in_minutes), sd_tt = sd(time_in_minutes) )

expdata.trialtimetaken <- expdata %>%
  select(participant, trial, rt) %>%
  group_by(participant) %>%
  summarize(sum_trials = sum(rt)) %>%
  ungroup () %>%
  summarize(mean_trials = mean(sum_trials), sd_trials = sd(sum_trials), mean_trials_mins = mean_trials/60000, sd_trials_mins = sd_trials/60000)
expdata.trialtimetaken
```

##ppts per experiment
```{r}
n_ppts <- expdata %>%
  select(participant, expcode) %>%
  unique() %>%
  group_by(expcode) %>%
  summarize(n = n())

n_ppts
```

## obs per stim per exp
```{r}
n_obs_stim_exp <- expdata %>%
  filter(criticality == 'CRITICAL') %>%
  select(participant, expcode, trial, condition) %>%
  unique() %>%
  group_by(expcode, trial,condition) %>%
  summarize(n = n()) %>%
  select(expcode, n, condition) %>%
  unique() 
n_obs_stim_exp
expdata
```